Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-02-26 code/paper.Rmd
graphs

@@

@@

>>>>

```{r}
# load the random pages
ten_k_random_wp_pages <- readRDS(here::here("data", "random_page_data_tbl.rds"))

ten_k_random_wp_pages_basic_qualities <- 
ten_k_random_wp_pages %>% 
  select(page_wordcount,
         page_wikilinks_out, 
         page_cited_items_on) %>% 
  mutate(rnd_page_wikilinks_out_per_1k_words = page_wikilinks_out / page_wordcount * 1000,
         rnd_page_cited_items_on_per_1k_words = page_cited_items_on / page_wordcount * 1000,
         rnd_page_wordcount = page_wordcount) %>% 
  select(-page_wikilinks_out,
         -page_cited_items_on,
         -page_wordcount)

ten_k_random_wp_pages_basic_qualities_long <- 
  ten_k_random_wp_pages_basic_qualities %>% 
  gather(variable, value) 
```

@@

```{r}
page_data_for_all_pages_basic_qualities <- 
page_data_for_all_pages %>% 
  select(page_wordcount,
         page_wikilinks_out, 
         page_cited_items_on) %>% 
  mutate(page_wikilinks_out_per_1k_words = page_wikilinks_out / page_wordcount * 1000,
         page_cited_items_on_per_1k_words = page_cited_items_on / page_wordcount * 1000) %>% 
  select(-page_wikilinks_out,
         -page_cited_items_on)

page_data_for_all_pages_basic_qualities_long <- 
page_data_for_all_pages_basic_qualities %>% 
  gather(variable, value) %>% 
  bind_rows(ten_k_random_wp_pages_basic_qualities_long) %>% 
  mutate(source = ifelse(str_detect(variable, "rnd" ), "10k Random pages", "World Heritage pages")) %>% 
  mutate(variable = str_remove(variable, "rnd_"))

# density plots
  ggplot(page_data_for_all_pages_basic_qualities_long,
         aes(value)) +
  geom_density(aes(fill = source),
               alpha = 0.3) +
  scale_x_log10() +
  scale_fill_viridis_d() +
  facet_wrap( ~ variable, 
              scales = "free") +
  theme_minimal()
```

```{r}
# scatterplots
  ggplot() +
      geom_point(data = ten_k_random_wp_pages_basic_qualities,
             aes(rnd_page_wikilinks_out_per_1k_words,
                 rnd_page_cited_items_on_per_1k_words,
                 size = rnd_page_wordcount),
             colour = "grey80",
             alpha = 0.4) +
  geom_point(data = page_data_for_all_pages_basic_qualities,
             aes(page_wikilinks_out_per_1k_words,
                 page_cited_items_on_per_1k_words,
                 size = page_wordcount),
             colour = "red",
             alpha = 0.8) +
  scale_x_log10() +
  scale_y_log10() +
  scale_fill_viridis_d() +
  coord_fixed() +
  theme_minimal()

@@

```{r}
ten_k_random_wp_pages_attent <- 
ten_k_random_wp_pages %>% 
  select(page_wikilinks_in, 
         page_views_last_n_days_total)

page_data_for_all_pages_attent <- 
page_data_for_all_pages %>% 
  select(page_wikilinks_in, 
         page_views_last_n_days_total)

page_data_for_all_pages %>% 
  select( Site,
         page_wikilinks_in, 
         page_views_last_n_days_total)  %>% 
  ggplot(aes(page_wikilinks_in,
             page_views_last_n_days_total,
             label = Site)) +
  geom_point(alpha = 0.4) +
    geom_text_repel(
    data          = page_data_for_all_pages %>%  
                           filter(page_views_last_n_days_total > 190000),
    segment.size  = 0.2,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10(expand = c(1, 0.05)) +
  scale_x_log10(limits = c(1, 10000)) +
  coord_fixed(0.5) +
  theme_minimal()

page_data_for_all_pages_attent_long <- 
page_data_for_all_pages_attent %>% 
  gather(variable, value) %>% 
  bind_rows(ten_k_random_wp_pages_attent %>% 
              gather(variable, value) %>% 
              mutate(variable =  str_glue('rnd_{variable}'))) %>% 
  mutate(source = ifelse(str_detect(variable, "rnd" ), "10k Random pages", 
                         "World Heritage pages")) %>% 
  mutate(variable = str_remove(variable, "rnd_"))

# density plots
  ggplot(page_data_for_all_pages_attent_long,
         aes(value)) +
  geom_density(aes(fill = source),
               alpha = 0.3) +
  scale_x_log10() +
  scale_fill_viridis_d() +
  facet_wrap( ~ variable, 
              scales = "free") +
  theme_minimal()
```
